Meta-analysis of the Interoceptive Accuracy Scale

### 2024-02-27 analysis/study1.qmd
update figs
@AnafNeves @magdapf I think we are close to a definitive version of the results, so we can focus on the paper
- TODO is to add the various samples tabs in study1 in some of the steps where I was too lazy to add them

p1 <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10a, dens10b) |>
  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10a", "Sample 10b")) |>
  # mutate(Dashed = ifelse(Parameter %in% c("Affective_touch", "Blood_Sugar", "Bruise"), TRUE, FALSE)) |> 
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line() +
  scale_color_material_d() +
  scale_linetype_manual(values = c("solid", "dashed"), guide="none") +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(face="bold")) +
  labs(title = "Distribution of responses for all items across various datasets", x = "Response", y = "Density", color = "Item") +
  facet_wrap(~Sample, scales = "free_y", nrow = 5)

>>>>

p1 <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10a, dens10b) |>
  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10a", "Sample 10b")) |>
  # mutate(Dashed = ifelse(Parameter %in% c("Affective_touch", "Blood_Sugar", "Bruise"), TRUE, FALSE)) |> 
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line() +
  scale_color_material_d() +
  scale_linetype_manual(values = c("solid", "dashed"), guide="none") +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(face="bold")) +
  labs(x = "Response", y = "Density",
       # title = "Distribution of responses for all items across various datasets", 
       color = "Item") +
  facet_wrap(~Sample, scales = "free_y", nrow = 5)

### 2024-02-27 analysis/study2.qmd
update figs
@AnafNeves @magdapf I think we are close to a definitive version of the results, so we can focus on the paper
- TODO is to add the various samples tabs in study1 in some of the steps where I was too lazy to add them

# names(df1a)
# names(df1b)
# names(df2)  # BPQ, BVAQ, MAIA, ICQ, TAS
# names(df3)  # TAS, BPQ
# names(df4)  # BAQ, BPQ, MAIA, BRS, PBCS
# names(df5)  
# names(df6)  # IATS, SSS, GAD, PHQ2
# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES (?)
# names(df7b)  # MAIA, STAI, BPQ, PHQ15, PHQ9
# names(df7c)  # TAS, BPQ, ASI, BDI, CI (?), IASV (?), IASP (?)
# names(df8a)  # EDI (eating disorder inventory?), BPQ
# names(df8b)  # TAS, PHQ15, PHQ9
# names(df9)  # BFI, STQ (?), EQ (?), ECR (?), TEAQ (?), UCLA (?), TACSEN (?)
# names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
# names(df10b)  # BDI, STAI, PHQ4
```

@@

Even EGA components capture pairs or groupings of pairs of items.

@@

## Body

@@

```{r}
# names(df2)[str_detect(names(df2), "MAIA")]  
# names(df4)[str_detect(names(df4), "MAIA")] 
# names(df7a)[str_detect(names(df7a), "MAIA")]  
# names(df7b)[str_detect(names(df7b), "maia")] 
# names(df10a)[str_detect(names(df10b), "MAIA")]

@@

### Body

@@

rez_bpq <- rbind(
  # df2
  make_cor(df2, vars_intero, with = "BPQ_A", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df2, vars_intero, with = "BPQ_R", component="Body") |>
    mutate(var_Correlate = "Autonomic Reactivity (BPQ)"),
  make_cor(df2, vars_intero, with = "ICQ", component="Body") |>
    mutate(var_Correlate = "Interoceptive Confusion (ICQ)"),
  # df3
  make_cor(df3, vars_intero, with = "BPQ_BodyAwareness", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df3, vars_intero, with = "BPQ_AutonomicReactivity", component="Body") |>
    mutate(var_Correlate = "Autonomic Reactivity (BPQ)"),
  # df4
  make_cor(df4, vars_intero, with = "BPQ_A", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df4, vars_intero, with = "BAQ", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BAQ)"),
  make_cor(df4, vars_intero, with = "PBCS", component="Body") |>
    mutate(var_Correlate = "Body Consciousness (PBCS)"),
  make_cor(df4, vars_intero, with = "BRS", component="Body") |>
    mutate(var_Correlate = "Body Responsiveness (BRS)"),
  # df 6
  make_cor(df6, vars_intero, with = "IATS_sum", component="Body") |>
    mutate(var_Correlate = "Interoceptive Attention (IATS)"),
  make_cor(df6, vars_intero, with = "SSS8_sum", component="Body") |>
    mutate(var_Correlate = "Somatic Burden (SSS-8)"),
  # df 7b
  make_cor(df7b, vars_intero, with = "BPQ_Sum", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df7b, vars_intero, with = "PHQ15_Sum", component="Mood") |>
    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
  # df 7c
  make_cor(df7c, vars_intero, with = "BPQ_sum", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df7c, vars_intero, with = "ICQ_sum", component="Body") |>
    mutate(var_Correlate = "Interoceptive Confusion (ICQ)"),
  # df8a
  make_cor(df8a, vars_intero, with = "BPQ_A", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)")
)

display_sig(rez_bpq)
```

@@

rez_alexi <- rbind(
  make_cor(df2, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_DescribingFeelings", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_IdentifyingFeelings", component="Alexithymia") |> 
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_ExternallyOrientedThinking", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_des", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ident", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ext", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  # BVAQ
  make_cor(df2, vars_intero, with = "BVAQ_Affective", component="Alexithymia") |>
    mutate(var_Correlate = "Affective (BVAQ)"),
  make_cor(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia") |>
    mutate(var_Correlate = "Cognitive (BVAQ)")
)

display_sig(rez_bpq)
```

@@

```{r}
# names(df6)[str_detect(names(df6), "PHQ")] 
# names(df7b)[str_detect(names(df7b), "PHQ")]
# names(df7c)[str_detect(names(df7c), "BDI")]
# names(df8b)[str_detect(names(df8b), "PHQ")]
# names(df9)

rez_dep <- rbind(
  make_cor(df6, vars_intero, with = "PHQ2_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-2)"),
  make_cor(df7b, vars_intero, with = "PHQ9_Sum", component="Mood")|>
    mutate(var_Correlate = "Depression (PHQ-9)"),
  make_cor(df7c, vars_intero, with = "BDI_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (BDI)"),
  make_cor(df8b, vars_intero, with = "PHQ15_sum", component="Mood") |>
    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
  make_cor(df8b, vars_intero, with = "PHQ9_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-9)"),
  make_cor(df10a, vars_intero, with = "PHQ4_Depression", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-2)"),
  make_cor(df10b, vars_intero, with = "BDI2_Total", component="Mood") |>
    mutate(var_Correlate = "Depression (BDI)")
)

@@

```{r}
rez_bpd <- rbind(
  make_cor(df10a, vars_intero, with = "BPD", component="Mood") |>
    mutate(var_Correlate = "Boderline Personality")
)

display_sig(rez_bpd)
```

@@

@@

```{r}
rez_gcbs <- rbind(
  make_cor(df10a, vars_intero, with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs") |>
    mutate(var_Correlate = "Extraterrestrial"),
  make_cor(df10a, vars_intero, with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs") |>
    mutate(var_Correlate = "Global Conspiracies"),
  make_cor(df10a, vars_intero, with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs") |>
    mutate(var_Correlate = "Government Malfeasance"),
  make_cor(df10a, vars_intero, with = "GCBS_InformationControl", component="Conspiracy Beliefs") |>
    mutate(var_Correlate = "Information Control"),
  make_cor(df10a, vars_intero, with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs") |>
    mutate(var_Correlate = "Personal Wellbeing")
)

@@

```{r}
# names(df4)

# rez_others <- rbind(
#   make_cor(df2, vars_intero, with = "ICQ", component="Other") |>
#     mutate(var_Correlate = "Interoceptive Confusion (ICQ)")
# )
# 
# display_sig(rez_others)
```

@@

```{r}
#| fig-height: 20
#| fig-width: 15

data <- rbind(
  rez_gender,
  rez_age,
  rez_maia,
  rez_bpq,
  rez_alexi,
  rez_dep,
  rez_anx,
  rez_bpd,
  rez_spq,
  rez_asq,
  rez_pers,
  rez_ffmq,
  rez_pi,
  rez_gcbs,
  rez_lie
)

p <- data |>
  mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S.")),
         dir = sign(r),
         var_Interoception = str_replace(var_Interoception, "CoughSneeze", "Cough/Sneeze"),
         var_Interoception = str_replace(var_Interoception, "HeartBreathing", "Heart/Breathing"),
         var_Interoception = str_replace(var_Interoception, "HungryThirsty", "Hungry/Thirsty"),
         var_Interoception = str_replace(var_Interoception, "ItchBruise", "Itch/Bruise"),
         var_Interoception = str_replace(var_Interoception, "MusclesPain", "Muscles/Pain"),
         var_Interoception = str_replace(var_Interoception, "UrinateDefecate", "Urinate/Defecate"),
         var_Interoception = str_replace(var_Interoception, "WindBurp", "Wind/Burp"),
         var_Interoception = str_replace(var_Interoception, "Expulsion_Sudden", "Expulsion - Sudden"),
         var_Interoception = fct_relevel(var_Interoception, "Heart/Breathing", "Muscles/Pain", "Itch/Bruise", "Hungry/Thirsty", "Urinate/Defecate", "Wind/Burp", "Cough/Sneeze")) |>
         # Component = fct_relevel(
         #   Component, "Demographic", "MAIA", "Body", "Mood", "Maladaptive",
         #   "Schizotypic", "Autistic", "Personality", "Conspiracy Beliefs", "World Beliefs", "Lying Profile")) |>
  ggplot(aes(y = var_Correlate)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  # geom_bar(aes(fill=Sample, alpha=sig, y=r, group=Sample), stat="identity", position = position_dodge2(width = 0.8)) +
  geom_linerange(aes(color=dir, alpha=sig, xmin=0, xmax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
  geom_linerange(aes(xmin = CI_low, xmax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7)) +
  scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_color_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_alpha_discrete(range = c(0.2, 0.7), guide = "none") +
  scale_x_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
  facet_grid(Component ~ var_Interoception, scales = "free_y", switch = "y") +
  coord_cartesian(xlim = c(-0.45, 0.45)) +
  theme_modern(axis.title.space = 5) +
  # labs(x = "Correlation", title="Correlates of the Interoceptive Accuracy Scale (IAS)") +
  theme(panel.grid.major.y = element_line(),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.line.x = element_blank(),
        axis.text.y = element_text(size = rel(0.5)),
        axis.text.x = element_text(size = rel(0.8)),
        plot.title = element_text(face = "bold", hjust = 0),
        strip.placement = "outside",
        strip.background.y = element_rect(fill = "#E0E0E0", color = "white"),
        strip.background.x = element_rect(fill = "#F8BBD0", color = "white"))
p
ggsave("figures/Figure2.png", p, width=21*0.6, height=29.7*0.45, dpi=200, bg="white")
```

## Discussion

Benefits of the IAS:
- Straightforward and sensation-centered items

Recommendations:
- Remove Itch (redundant + issue in Chinese)
- Use analog scales

Limitations:
- Not much clear theorethical or empirical structure (small grouping of items)
- Limited variability (clear mode at 4/5), very low prevalence of 5/5 responses.
- Ambiguous items which grouping depends on the context (and its awareness)
  - E.g., heart beating fast, vomit when nauseaous
- Few items for some modalities (e.g., 1 for heart)
- Positive phrasing: benefits but also might exacerbate positivity bias (and thus unidimensionality)

Need for context-specific items (cross-modal when possible, i.E., cardioception, respiroception, etc.).

New Scale: Multimodal Interoceptive Sensitivity Scale (MISS)

>>>>

# names(df1a)
# names(df1b)
# names(df2)  # BPQ, BVAQ, MAIA, ICQ, TAS
# names(df3)  # TAS, BPQ
# names(df4)  # BAQ, BPQ, MAIA, BRS, PBCS
# names(df5)  
# names(df6)  # IATS, SSS, GAD, PHQ2
# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES
# names(df7b)  # MAIA, STAI, BPQ, PHQ15, PHQ9
# names(df7c)  # TAS, BPQ, ASI, BDI, CI (?), IASV (?), IASP (?)
# names(df8a)  # EDI (eating disorder inventory?), BPQ
# names(df8b)  # TAS, PHQ15, PHQ9
# names(df9)  # BFI, STQ (?), EQ, ECR, TEAQ, UCLA, TACSEN
# names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
# names(df10b)  # BDI, STAI, PHQ4
```

@@

Very strong correlations between empirical scores (i.e., average of pairs of items) and dimensions derived from models. Even EGA components capture pairs or groupings of pairs of items.

@@

## Interoception

@@

```{r}
# names(df2)[str_detect(names(df2), "MAIA")]  
# names(df4)[str_detect(names(df4), "MAIA")] 
# names(df7a)[str_detect(names(df7a), "MAIA")]  
# names(df7b)[str_detect(names(df7b), "maia")] 
# names(df8a)[str_detect(names(df8a), "EDI")] 
# names(df10a)[str_detect(names(df10b), "MAIA")]

@@

### Body Awareness

@@

rez_body <- rbind(
  # df2
  make_cor(df2, vars_intero, with = "BPQ_A", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df2, vars_intero, with = "BPQ_R", component="Body") |>
    mutate(var_Correlate = "Autonomic Reactivity (BPQ)"),
  make_cor(df2, vars_intero, with = "ICQ", component="Body") |>
    mutate(var_Correlate = "Interoceptive Confusion (ICQ)"),
  # df3
  make_cor(df3, vars_intero, with = "BPQ_BodyAwareness", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df3, vars_intero, with = "BPQ_AutonomicReactivity", component="Body") |>
    mutate(var_Correlate = "Autonomic Reactivity (BPQ)"),
  # df4
  make_cor(df4, vars_intero, with = "BPQ_A", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df4, vars_intero, with = "BAQ", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BAQ)"),
  make_cor(df4, vars_intero, with = "PBCS", component="Body") |>
    mutate(var_Correlate = "Body Consciousness (PBCS)"),
  make_cor(df4, vars_intero, with = "BRS", component="Body") |>
    mutate(var_Correlate = "Body Responsiveness (BRS)"),
  # df 6
  make_cor(df6, vars_intero, with = "IATS_sum", component="Body") |>
    mutate(var_Correlate = "Interoceptive Attention (IATS)"),
  make_cor(df6, vars_intero, with = "SSS8_sum", component="Body") |>
    mutate(var_Correlate = "Somatic Burden (SSS-8)"),
  # df 7b
  make_cor(df7b, vars_intero, with = "BPQ_Sum", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df7b, vars_intero, with = "PHQ15_Sum", component="Mood") |>
    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
  # df 7c
  make_cor(df7c, vars_intero, with = "BPQ_sum", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df7c, vars_intero, with = "ICQ_sum", component="Body") |>
    mutate(var_Correlate = "Interoceptive Confusion (ICQ)"),
  # df8a
  make_cor(df8a, vars_intero, with = "BPQ_A", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df8a, vars_intero, with = "EDI_IA", component="Body") |>
    mutate(var_Correlate = "Interoceptive Awareness (EDI)")
)

display_sig(rez_body)
```

@@

rez_alexi <- rbind(
  make_cor(df2, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Diff. Identifying Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Diff. Describing Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_DescribingFeelings", component="Alexithymia") |>
    mutate(var_Correlate = "Diff. Describing Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_IdentifyingFeelings", component="Alexithymia") |> 
    mutate(var_Correlate = "Diff. Identifying Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_ExternallyOrientedThinking", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_des", component="Alexithymia") |>
    mutate(var_Correlate = "Diff. Describing Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ident", component="Alexithymia") |>
    mutate(var_Correlate = "Diff. Identifying Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ext", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Diff. Identifying Feelings (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Diff. Describing Feelings (TAS)"),
  # BVAQ
  make_cor(df2, vars_intero, with = "BVAQ_Affective", component="Alexithymia") |>
    mutate(var_Correlate = "Affective (BVAQ)"),
  make_cor(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia") |>
    mutate(var_Correlate = "Cognitive (BVAQ)")
)

display_sig(rez_alexi)
```

@@

```{r}
# names(df6)[str_detect(names(df6), "PHQ")] 
# names(df7a)[str_detect(names(df7aa), "PHQ")]
# names(df7b)[str_detect(names(df7b), "PHQ")]
# names(df7c)[str_detect(names(df7c), "BDI")]
# names(df8b)[str_detect(names(df8b), "PHQ")]
# names(df9)

rez_dep <- rbind(
  make_cor(df6, vars_intero, with = "PHQ2_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-2)"),
  make_cor(df7a, vars_intero, with = "CES_SUM", component="Mood")|>
    mutate(var_Correlate = "Depression (CES)"),
  make_cor(df7b, vars_intero, with = "PHQ9_Sum", component="Mood")|>
    mutate(var_Correlate = "Depression (PHQ-9)"),
  make_cor(df7c, vars_intero, with = "BDI_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (BDI)"),
  make_cor(df8b, vars_intero, with = "PHQ15_sum", component="Mood") |>
    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
  make_cor(df8b, vars_intero, with = "PHQ9_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-9)"),
  make_cor(df10a, vars_intero, with = "PHQ4_Depression", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-2)"),
  make_cor(df10b, vars_intero, with = "BDI2_Total", component="Mood") |>
    mutate(var_Correlate = "Depression (BDI)")
)

@@

@@

```{r}
# names(df9)[str_detect(names(df9), "UCLA")]
# names(df9)[str_detect(names(df9), "EQ")]
df9$EQ <- rowMeans(select(df9, starts_with("EQ")))

rez_social <- rbind(
  make_cor(df9, vars_intero, with = "UCLA_TOTAL", component="Interpersonal") |>
    mutate(var_Correlate = "Loneliness (UCLA)"),
  make_cor(df9, vars_intero, with = "EQ", component="Interpersonal") |>
    mutate(var_Correlate = "Empathy (EQ)"),
  make_cor(df9, vars_intero, with = "ECR_ANXIETY", component="Interpersonal") |>
    mutate(var_Correlate = "Relationship Anxiety (ECR)"),
  make_cor(df9, vars_intero, with = "ECR_AVOIDANCE", component="Interpersonal") |>
    mutate(var_Correlate = "Relationship Avoidance (ECR)"),
  make_cor(df10a, vars_intero, with = "BPD", component="Interpersonal") |>
    mutate(var_Correlate = "Boderline Personality")
)

display_sig(rez_social)
```

@@

```{r}
rez_gcbs <- rbind(
  make_cor(df10a, vars_intero, with = "GCBS_Extraterrestrial", component="Conspiracy") |>
    mutate(var_Correlate = "Extraterrestrial"),
  make_cor(df10a, vars_intero, with = "GCBS_GlobalConspiracies", component="Conspiracy") |>
    mutate(var_Correlate = "Global Conspiracies"),
  make_cor(df10a, vars_intero, with = "GCBS_GovernmentMalfeasance", component="Conspiracy") |>
    mutate(var_Correlate = "Government Malfeasance"),
  make_cor(df10a, vars_intero, with = "GCBS_InformationControl", component="Conspiracy") |>
    mutate(var_Correlate = "Information Control"),
  make_cor(df10a, vars_intero, with = "GCBS_PersonalWellbeing", component="Conspiracy") |>
    mutate(var_Correlate = "Personal Wellbeing")
)

@@

@@

```{r}
#| fig-height: 13.365
#| fig-width: 9.45
#| fig-cap: "Subjective Correlates of the Interoceptive Accuracy Scale (IAS). Each bar represents one sample (total N = **TODO**), and different samples using the same measures are grouped together, providing an intuition of the general trend. Blue and red bars represent positive and negative correlations, respectively, with their 95% CI. Transparent bars indicate non-significant correlations (p > .05)."

data <- rbind(
  rez_gender,
  rez_age,
  rez_maia,
  rez_body,
  rez_alexi,
  rez_dep,
  rez_anx,
  rez_spq,
  rez_asq,
  rez_pid,
  rez_social,
  rez_pers,
  rez_ffmq,
  rez_pi,
  rez_gcbs,
  rez_lie
)

p <- data |>
  mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S.")),
         dir = sign(r),
         var_Interoception = str_replace(var_Interoception, "CoughSneeze", "Cough/Sneeze"),
         var_Interoception = str_replace(var_Interoception, "HeartBreathing", "Heart/Breathing"),
         var_Interoception = str_replace(var_Interoception, "HungryThirsty", "Hungry/Thirsty"),
         var_Interoception = str_replace(var_Interoception, "ItchBruise", "Itch/Bruise"),
         var_Interoception = str_replace(var_Interoception, "MusclesPain", "Muscles/Pain"),
         var_Interoception = str_replace(var_Interoception, "UrinateDefecate", "Urinate/Defecate"),
         var_Interoception = str_replace(var_Interoception, "WindBurp", "Wind/Burp"),
         var_Interoception = str_replace(var_Interoception, "Expulsion_Sudden", "Expulsion - Sudden"),
         var_Interoception = fct_relevel(var_Interoception, "Heart/Breathing", "Muscles/Pain", "Itch/Bruise", "Hungry/Thirsty", "Urinate/Defecate", "Wind/Burp", "Cough/Sneeze"),
         Component = fct_relevel(
           Component, "Demographic", "MAIA", "Body", "Alexithymia", "Mood", "Maladaptive",
           "Schizotypic", "Autistic", "Interpersonal", "Personality", "Conspiracy", "World Beliefs", "Lying Profile", "Mindfulness")) |>
  ggplot(aes(y = var_Correlate)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  # geom_bar(aes(fill=Sample, alpha=sig, y=r, group=Sample), stat="identity", position = position_dodge2(width = 0.8)) +
  geom_linerange(aes(color=dir, alpha=sig, xmin=0, xmax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2) +
  geom_linerange(aes(xmin = CI_low, xmax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7)) +
  scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_color_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_alpha_discrete(range = c(0.2, 0.7), guide = "none") +
  scale_x_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
  facet_grid(Component ~ var_Interoception, scales = "free_y", switch = "y") +
  coord_cartesian(xlim = c(-0.45, 0.45)) +
  theme_modern(axis.title.space = 5) +
  # labs(x = "Correlation", title="Correlates of the Interoceptive Accuracy Scale (IAS)") +
  theme(panel.grid.major.y = element_line(),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.line.x = element_blank(),
        axis.text.y = element_text(size = rel(0.5)),
        axis.text.x = element_text(size = rel(0.8)),
        plot.title = element_text(face = "bold", hjust = 0),
        strip.placement = "outside",
        strip.background.y = element_rect(fill = "#E0E0E0", color = "white"),
        strip.background.x = element_rect(fill = "#F8BBD0", color = "white"))
p
ggsave("figures/Figure2.png", p, width=21*0.45, height=29.7*0.45, dpi=200, bg="white")
```
